Do I Need to Model You in order to Learn With You?

### 2015-04-02 mutual-modeling.tex
Done with proof-reading of sections 1, 2 and 3

Our main issue is the symmetry questions: what is the relationship
(Fig.~\ref{mm_symmetry}) between \Model{A}{B}{X} and \Model{B}{A}{X}? A low
symmetry would mean that mutual modelling is mainly an individual
attitude/aptitude ($\mathcal{H}_{1}$). A high correlation might support
$\mathcal{H}_{2}$ since there is a low probability that randomly formed pairs
integrate peers with the same level of mutual modelling skills.

@@

This leads to two \emph{triangle questions} (Fig.~\ref{mm_triangles}): Do $A$ and
B have the same accuracy when modelling C? $\Delta_2 = \Delta(\M{A}{C}{X},
\M{B}{C}{X})$. If it is the same, $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$ gain
over $\mathcal{H}_{1}$

@@

We could go further by comparing self- versus other modelling ($\Delta_4$ in
Fig.~\ref{mm_rectangle}) as an indication of meta-cognitive skills. We can also
question if modelling skills depend upon what aspects are being modeled ($X$ or $Y$),
which would explain vertical differences ($\Delta_5$ in
Fig.~\ref{mm_rectangle}). We do not however further develop these questions because we
don't have the necessary data in our studies.

@@

\subsubsection*{Questions}

@@

\paragraph{Symmetry question} We computed intra-class correlation as described
by~\citep{kenny1998data} from the answers to the cross-questionnaires.
Considering all pairs in both conditions, we found a positive and significant
correlation ($r = .38, p < .05$) between \gModel{A}{B} and \gModel{B}{A}.
Interestingly, this was higher in the control group ($r = 0.44$) than in the
experimental group ($r = 0.24$). Actually, $\Delta(\gMdeg{A}{B},\gMdeg{B}{A})$,
\ie the absolute differences between the models accuracy, was not significantly
different with or without the awareness tool ($F [1,13]= 0.144, p > 0.5$). This
result could be explained by the fact that the players without awareness tools
communicated more.

@@

\subsubsection*{Questions}

This study investigated the effect of a collaboration script on collaborative
learning~\citep{molinari2008effects}. The script chosen is a JIGSAW: two students
receive different but complementary subsets of the knowledge (texts) which have
to be integrated to build a shared concept map.  This script increases the
cognitive effort to build the map, not only to recon ciliate the viewpoints of
each team members but, before that, to find out what the other knows.

@@

The peers were located into two different rooms. A complete description of the
study is provided in~\citep{sangin2008learners}. The experiment lasted 90 minutes.

>>>>

One interesting question relates to the symmetry of mutual modelling: what is
the relationship between \Model{A}{B}{X} and
\Model{B}{A}{X} (Fig.~\ref{mm_symmetry})? A low symmetry would mean that mutual modelling is mainly an
individual attitude/aptitude ($\mathcal{H}_{1}$). A high correlation might
support $\mathcal{H}_{2}$ since there is a low probability that randomly formed
pairs integrate peers with the same level of mutual modelling skills.

@@

This leads to two \emph{triangle questions} (Fig.~\ref{mm_triangles}): Do $A$ and
B have the same accuracy when modelling C? $\Delta_2 = \Delta(\M{A}{C}{X},
\M{B}{C}{X})$. If it is the same, $\mathcal{H}_{2}$ and
$\mathcal{H}_{3}$\fxfatal{why H3?} gain
over $\mathcal{H}_{1}$

@@

We could go further by comparing self- versus other modelling ($\Delta_4$ in
Fig.~\ref{mm_rectangle}) as an indication of meta-cognitive skills. We can also
question if modelling skills depend upon what aspects are being modeled ($X$ or
$Y$), which would explain vertical differences ($\Delta_5$ in
Fig.~\ref{mm_rectangle}). We do not however further explore these questions
since we do not have the necessary data in our studies.

@@

@@

\paragraph{Symmetry question} We computed intra-class correlation as described
by~\citet{kenny1998data} from the answers to the cross-questionnaires.
Considering all pairs in both conditions, we found a positive and significant
correlation ($r = .38, p < .05$) between \gModel{A}{B} and \gModel{B}{A}.
Interestingly, this was higher in the control group ($r = 0.44$) than in the
experimental group ($r = 0.24$). Actually, $\Delta(\gMdeg{A}{B},\gMdeg{B}{A})$,
\ie the absolute differences between the models accuracy, was not significantly
different with or without the awareness tool ($F [1,13]= 0.144, p > 0.5$). This
result could be explained by the fact that the players without awareness tools
communicated more.

@@

This study investigated the effect of a collaboration script on collaborative
learning~\citep{molinari2008effects}. The script chosen is a {\sc jigsaw}: two students
receive different but complementary subsets of the knowledge (texts) which have
to be integrated to build a shared concept map.  This script increases the
cognitive effort to build the map, not only to recon ciliate the viewpoints of
each team members but, before that, to find out what the other knows.

@@

The peers were located into two different rooms. A complete description of the
study is provided in~\citet{sangin2008learners}. The experiment lasted 90 minutes.
